Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
missing references

To filter more noise before computing the partial correlation, we kept
$80\%$ of the eigen vectors which have the largest eigen
value (\cite{tipping1999mixtures}). In the context of the challenge, this
assumption was deduced from ground truth of provided networks.

>>>>

To filter even more noise before computing the partial correlation, we kept
$80\%$ of the eigen vectors which have the largest eigen
value (\cite{tipping1999mixtures}). In the context of the challenge, this
assumption was deduced from ground truth of provided networks.
